Regular singular Volterra equations on complex domains

### 2023-08-31 reg-sing-volterra.tex
Do some rewording in example section

\begin{rmk}
In the relationship between $\fracderiv{-\nu}{\zeta}{\alpha}$ and multiplication by $z^{-\nu}$ described above, smoothing out the singularity at $\zeta = \alpha$ in the position domain corresponds to speeding up the decay as $|z| \to \infty$ in the frequency domain. This is a general feature of the Laplace transform.
\end{rmk}
\subsection{Going to the position domain}
By the properties of the Laplace transform $\laplace_{\zeta,\alpha}^{\theta}$ we can turn differential operators in the frequency domain into Volterra operators in the position domain. 
\begin{lemma}\label{lem:use-dict}
For each root $-\alpha$ of $P$, let $\hat{\mathcal{P}}_{\alpha}$ be the Volterra operator 
\[ \hat{\mathcal{P}}_\alpha:=P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha}^{-2}\circ R(\partial_{\zeta,\alpha}^{-1}). \]
If $\psi_\alpha$ satisfies the equation $\hat{\mathcal{P}}_\alpha\psi_\alpha=0$, then its Laplace transform $\Psi_\alpha:=\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha$ satisfies the equation $\mathcal{P}\Psi_\alpha=0$, as long as the Laplace transform is well-defined.
\end{lemma}

\begin{rmk}
For the Laplace transform to have any hope of being well-defined, we have to choose the direction $\theta$ so that the ray $\Gamma_{\zeta, \alpha}^\theta$ stays within $\domain_\alpha$. We'll see later that for our results to apply, $\domain_\alpha$ can't touch any zero of $P(-\zeta)$ other than $\zeta = \alpha$. For instance, $\domain_\alpha$ looks like the domain drawn in Section \ref{setting:domain}, replacing the origin $\zeta=0$ with $\zeta=\alpha$. 
\end{rmk}
\begin{proof}[Proof of Lemma~\ref{lem:use-dict}]
Comparing the definitions of $\mathcal{P}$ and $\hat{\mathcal{P}}_\alpha$, and using the properties of the Laplace transform discussed in Section~\ref{sec:L-int-op}, we can work out that $\mathcal{P} \laplace_{\zeta,\alpha}^\theta = \laplace_{\zeta,\alpha}^\theta \hat{\mathcal{P}}_\alpha$. Hence,
\begin{align*}
\mathcal{P}\Psi_\alpha & = \mathcal{P}\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha \\
& = \laplace_{\zeta,\alpha}^{\theta}\hat{\mathcal{P}}_\alpha\psi_\alpha.
\end{align*}
\end{proof}

>>>>

\begin{rmk}
In the relationship between $\fracderiv{-\nu}{\zeta}{\alpha}$ and multiplication by $z^{-\nu}$ described above, smoothing out the singularity at $\zeta = \alpha$ in the position domain corresponds to speeding up the decay as $|z| \to \infty$ in the frequency domain. This is a general feature of the Laplace transform.
\end{rmk}
\subsection{Going to the position domain}
Using the properties of the Laplace transform $\laplace_{\zeta,\alpha}^{\theta}$ we can turn differential operators in the frequency domain into Volterra operators in the position domain. 
\begin{lemma}\label{lem:use-dict}
For each root $-\alpha$ of $P$, let $\hat{\mathcal{P}}_{\alpha}$ be the Volterra operator 
\[ \hat{\mathcal{P}}_\alpha:=P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha}^{-2}\circ R(\partial_{\zeta,\alpha}^{-1}). \]
If $\psi_\alpha$ satisfies the equation $\hat{\mathcal{P}}_\alpha\psi_\alpha=0$, then its Laplace transform $\Psi_\alpha:=\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha$ satisfies the equation $\mathcal{P}\Psi_\alpha=0$, as long as the Laplace transform is well-defined.
\end{lemma}

\begin{rmk}
For the Laplace transform to have any hope of being well-defined, we have to choose the direction $\theta$ so that the ray $\Gamma_{\zeta, \alpha}^\theta$ stays within $\domain_\alpha$. We'll see later that for our results to apply, $\domain_\alpha$ can't touch any zero of $P(-\zeta)$ other than $\zeta = \alpha$. As a result, $\domain_\alpha$ might look like the domain illustrated in Section \ref{setting:domain}, reinterpreting the origin as $\zeta = \alpha$. 
\end{rmk}
\begin{proof}[Proof of Lemma~\ref{lem:use-dict}]
Comparing the definitions of $\mathcal{P}$ and $\hat{\mathcal{P}}_\alpha$, and using the properties of the Laplace transform discussed in Section~\ref{sec:L-int-op}, we can work out that $\mathcal{P} \laplace_{\zeta,\alpha}^\theta = \laplace_{\zeta,\alpha}^\theta \hat{\mathcal{P}}_\alpha$. Hence,
\begin{align*}
\mathcal{P}\Psi_\alpha & = \mathcal{P}\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha \\
& = \laplace_{\zeta,\alpha}^{\theta}\hat{\mathcal{P}}_\alpha\psi_\alpha.
\end{align*}
\end{proof}
